Bayesian Hierarchical Models for Common Components across Multiple System Configurations

### 2017-09-09 paperDraft2.tex
small changes

\subsubsection{JLTV Reliability}
So far we have discussed a number of different models and the assumptions that
accompany them.  Using McMC we can fit each of these models to the JLTV dataset.
Then we can use the posterior distributions of the systems parameters to
estimate reliability-related quantities of interest.

Plot with expected miles to failure for each of 3 models to show the Weibull and
exponential give very different results.

>>>>

\subsubsection{JLTV Reliability}
So far we have discussed a number of different models and the assumptions that
accompany them.  Using McMC we can fit each of these models to the JLTV dataset.
Then we can use the posterior distributions of the systems parameters to
estimate reliability-related quantities of interest for each of the eight
vehicle types.  We are able to look at a number of different statistics related
to reliability at both  the component and system level.  In this study our main
quantity of interest is expected miles to  failure.  In the following figure we
have box plots showing the posterior distributions of  the expected miles to
failure for one of the vehicle types for each of the three  phases using each of
the three models we are considering.
